clusters

### 2015-10-07 Regression.rmd
BN prep

```{r echo=FALSE}
some <- all7d %>% select(return.pdol, mlsto, inv.mlsto, timespan,no.users,Discipline,pc.pro,
                         client.totinv,code.director,Num.disc,Business,Biz.type,
                         code.contact,code.client,Project.Value,JD.Second,Post.Code,code.ProjEng,Billing.Type,majority.pos,
                         pc.majpos)

@@

RMSE<- function(answer, guess){
        error= answer-guess
        root.error= sqrt(mean(error^2))
        # print(root.error)
}

final.output<- function(df=all7d, samp = 600) {
        #create sample df
        sample = df[samp,]
        sample = sample[,!is.na(sample)]
        vars= names(sample)
        vars = vars[! vars %in% c('mlsto','Year','inv.mlsto','timespan','client.totinv','code.director','Num.disc',
                                  'Biz.type','Post.Code','code.ProjEng','return.pdol','cost.mlsto','hrs.mlsto',
                                  'balance.mlsto','client.totinv.log','pc.majpos')]
        variables = vars

@@

        cats= c('code.client', 'code.contact', 'JD.Second', 'Business', 'Discipline', 'majority.pos')

@@

>>>>

```{r echo=FALSE}
some <- all7d %>% select(return.pdol, mlsto, inv.mlsto, timespan,no.users,Discipline,pc.pro,
                         client.totinv,code.director,Num.disc,Business,Biz.type,
                         code.contact,code.client,Project.Value,JD.Second,Post.Code,code.ProjEng,Billing.Type,
                         majority.pos,
                         pc.majpos)

@@

#make new dataframe for future use with normalised variables and variables that you want to use only
all8a<- all7d %>% select(no.users, Discipline, pc.pro, Business, code.client, JD.Second, timespan.cbrt,
                         inv.mlsto.log,client.totinv.log, pc.majpos.log, code.contact, Billing.Type,
                         majority.pos, return.pdol, mlsto, Year)
write.csv(all8a, 'C:/Users/n9232371/Documents/Consultbusiness/data/all8a.csv')

final.output<- function(df=all7d, samp = 800) {
        #create sample df
        sample = df[samp,]
        sample = sample[,!is.na(sample)]
        vars= names(sample)
        vars = vars[! vars %in% c('mlsto','Year','inv.mlsto','timespan','client.totinv','code.director','Num.disc',
                                  'Biz.type','Post.Code','code.ProjEng','return.pdol','cost.mlsto','hrs.mlsto',
                                  'dis.sc.mlsto',
                                  'balance.mlsto','client.totinv.log','pc.majpos')]
        variables = vars

@@

        cats= c('code.client', 'code.contact', 'JD.Second', 'Business', 'no.users', 'majority.pos')

@@

        num.cats= c('timespan.cbrt', 'inv.mlsto.log', 'pc.pro')

        for(i in 1:length(num.cats)){
                if(num.cats[i] %in% vars){
                        span = 0.05*(max(reduced[,num.cats][i])-min(reduced[,num.cats[i]]))
                        range = c(df[samp,num.cats[i]]-span, 
                                  df[samp,num.cats[i]]+span)
                        cats.red = reduced[reduced[,num.cats[i]]<range[2] & reduced[,num.cats[i]]>range[1],]
                        cat.RMSE = RMSE(cats.red$return.pdol, cats.red$predict) %>% round(4)
                        print(
                                paste(num.cats[i], "RMSE =", cat.RMSE, sep= " "))
                        print(
                                paste("Number of cases =", nrow(cats.red), sep= " "))
                        print(
                                if(num.cats[i] == 'pc.pro'){
                                        head(cats.red[,c('mlsto','inv.mlsto','cost.mlsto','return.pdol','predict',
                                                 num.cats[i])])} 
                                else if(num.cats[i] == 'timespan.cbrt'){
                                                head(cats.red[,c('mlsto','inv.mlsto','cost.mlsto',
                                                                 'return.pdol','predict', 'timespan')])}
                                else {
                                        head(cats.red[,c('mlsto','inv.mlsto','cost.mlsto',
                                                                 'return.pdol','predict')])
                                }

                        )}
        }

### 2015-10-07 cluster.rmd
BN prep

library('knitr', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('ggplot2', lib = 'C:/Progra~1/R/R-3.2.1/library')
library("plyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library("dplyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library('magrittr',lib='C:/Progra~1/R/R-3.2.1/library')
# library('reshape2',lib='C:/Progra~1/R/R-3.2.1/library')
# library("rpart",lib = 'C:/Program Files/R/R-3.2.1/library')
library('car', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('e1071', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('corrgram', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('party', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('randomForest', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('fpc', lib='C:/Progra~1/R/R-3.2.1/library')
# library('vegan', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library(devtools,lib='C:/Progra~1/R/R-3.2.1/library')
# library('ggbiplot',lib='C:/Progra~1/R/R-3.2.1/library')
# library('RcmdrPlugin.BCA',lib='C:/Progra~1/R/R-3.2.1/library')
# library('FNN', lib='C:/Progra~1/R/R-3.2.1/library')
# library('caret', lib='C:/Progra~1/R/R-3.2.1/library')

@@

all7d<- all7c %>% select(mlsto, Year, inv.mlsto, timespan, no.users, Discipline, pc.pro, 
                         client.totinv, code.director, 
                         Num.disc, Business,
                         Biz.type, code.contact, pc.majpos,
                         code.client, Project.Value, JD.Second, Post.Code, code.ProjEng, 
                         Billing.Type, majority.pos, return.pdol, cost.mlsto, hrs.mlsto, balance.mlsto)
all7d$mlsto<- as.character(all7d$mlsto)

@@

>>>>

library('knitr', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('ggplot2', lib = 'C:/Progra~1/R/R-3.2.1/library')
library("plyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library("dplyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library('magrittr',lib='C:/Progra~1/R/R-3.2.1/library')
# library('reshape2',lib='C:/Progra~1/R/R-3.2.1/library')
# library("rpart",lib = 'C:/Program Files/R/R-3.2.1/library')
library('car', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('e1071', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('corrgram', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('party', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('randomForest', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('fpc', lib='C:/Progra~1/R/R-3.2.1/library')
# library('vegan', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library(devtools,lib='C:/Progra~1/R/R-3.2.1/library')
library('ggbiplot',lib='C:/Progra~1/R/R-3.2.1/library')
# library('RcmdrPlugin.BCA',lib='C:/Progra~1/R/R-3.2.1/library')
# library('FNN', lib='C:/Progra~1/R/R-3.2.1/library')
# library('caret', lib='C:/Progra~1/R/R-3.2.1/library')

@@

all7d<- all7c %>% select(mlsto, Year, inv.mlsto, timespan, no.users, Discipline, pc.pro, 
                         client.totinv, code.director, 
                         Num.disc, Business,
                         Biz.type, code.contact, pc.majpos, dis.sc.mlsto
                         code.client, Project.Value, JD.Second, Post.Code, code.ProjEng, 
                         Billing.Type, majority.pos, return.pdol, cost.mlsto, hrs.mlsto, balance.mlsto)
all7d$mlsto<- as.character(all7d$mlsto)

@@

Adjust inv.mlsto, cost.mlsto, balance.mlsto, for inflation!!!!

library('quantmod', lib= 'C:/Progra~1/R/R-3.2.2/library')
getSymbols("CPIAUCSL", src='FRED') #Consumer Price Index for All Urban Consumers: All Items
#[1] "CPIAUCSL"
tail(CPIAUCSL)

# make an df object of costs
p<- data.frame('Year' = all7d$Year, 'inv.mlsto'= all7d$inv.mlsto, 'balance.mlsto' = all7d$balance.mlsto,
               'cost.mlsto' = all7d$cost.mlsto, 'mlsto' = all7d$mlsto, 'dis.sc.mlsto'=all7d$dis.sc.mlsto)

#calculate annual averave inflation since 2004
avg.cpi <- apply.yearly(CPIAUCSL, mean)
#ratio using 2014 as base year
cf <- avg.cpi/as.numeric(avg.cpi['2014'])
#create new cf column for date and extract year
cf<- as.data.frame(cf)
cf$Date<- rownames(cf)
cf$Date<- cf$Date %>% as.Date()
cf$Date<- format(cf$Date,"%Y")
p<- merge(p, cf, by.x='Year', by.y= 'Date')
#divide all dollar values by CPIAUCSL column
p<- transform(p, adj.inv.mlsto = inv.mlsto/CPIAUCSL,
          adj.balance.mlsto = balance.mlsto/CPIAUCSL,
          adj.cost.mlsto = cost.mlsto/CPIAUCSL,
          adj.dis.sc = dis.sc.mlsto/CPIAUCSL)
#check
s<- sample(1:nrow(all7d),10)
p[s,]
#replace existing all7d columns
all7d<- merge(all7d, p %>% select(mlsto, adj.inv.mlsto, adj.balance.mlsto, adj.cost.mlsto, adj.dis.sc), by='mlsto')
all7d<- all7d %>% select(-inv.mlsto, - balance.mlsto, -cost.mlsto, -dis.sc.mlsto)
colnames(all7d)[names(all7d) %in% "adj.inv.mlsto"] <- "inv.mlsto"
colnames(all7d)[names(all7d) %in% "adj.balance.mlsto"] <- "balance.mlsto"
colnames(all7d)[names(all7d) %in% "adj.cost.mlsto"] <- "cost.mlsto"
colnames(all7d)[names(all7d) %in% "adj.dis.sc"] <- "dis.sc.mlsto"

write.csv(all7d, 'all7d.csv')
